### 2016-03-15 paper.tex
Copy all references into paper.tex; resolves #15

% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
%
\bibliographystyle{plos2015}
\bibliography{library}

>>>>

% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
%
\bibliographystyle{plos2015}
\begin{thebibliography}{10}

    \bibitem{Neary2014}
    Neary VS, Previsic M, Jepsen RA, Lawson MJ, Yu YH, Copping AE, et~al.
    \newblock Methodology for Design and Economic Analysis of Marine Energy
    Conversion ({MEC}) Technologies.
    \newblock Albuquerque, NM, USA: Sandia National Laboratories; 2014.
    SAND2014-9040.

    \bibitem{Neary2014a}
    Neary VS, Lawson M, Previsic M, Copping A, Hallett KC, A L, et~al.
    \newblock Methodology for design and economic analysis of marine energy
    conversion (MEC) technologies.
    \newblock In: Proceedings of the Marine Energy Technology Symposium (METS2014).
    Seattle, WA; 2014. .

    \bibitem{Barone2011}
    Barone M, Griffith T, Berg J.
    \newblock Reference Model 2: ``Rev 0'' Rotor Design.
    \newblock Sandia National Laboratories; 2011. SAND2011-9306.

    \bibitem{Neary2011}
    Neary VS.
    \newblock Reference inflow characterization for river resource reference model
    (RM2).
    \newblock Oak Ridge National Laboratory; 2011. ORNL/TM-2011/360.
    \newblock Available from:
    \url{http://info.ornl.gov/sites/publications/files/Pub32455.pdf}.

    \bibitem{Murray2011}
    Murray J, Barone M.
    \newblock The Development of CACTUS, a Wind and Marine Turbine Performance
    Simulation Code.
    \newblock In: Proceedings of the 49th AIAA Aerospace Sciences Meeting including
    the New Horizons Forum and Aerospace Exposition; 2011. .

    \bibitem{Hill2014}
    Hill C, Neary V, Gunawan B, Guala M, Sotiropoulos F.
    \newblock {U.S.} {D}epartment of {E}nergy {R}eference {M}odel {P}rogram {RM2}:
    Experimental Results.
    \newblock St. Anthony Falls Laboratory for Wind and Water Technologies Program,
    Office of Energy Efficiency and Renewable Energy, U.S. Department of Energy;
    2014.

    \bibitem{Blackwell1976}
    Blackwell B, Sheldahl R, Feltz L.
    \newblock Wind Tunnel Performance Data for the {Darrieus} Wind Turbine with
    {NACA} 0012 Blades.
    \newblock Albuquerque, {NM}: Sandia National Laboratories; 1976. SAND76-0130.

    \bibitem{Bachant2014}
    Bachant P, Wosnik M.
    \newblock Reynolds Number Dependence of Cross-Flow Turbine Performance and
    Near-Wake Characteristics.
    \newblock In: Proceedings of the 2nd Marine Energy Technology Symposium
    METS2014. Seattle, WA; 2014. Available from:
    \url{http://hdl.handle.net/10919/49210}.

    \bibitem{Bachant2016-RVAT-Re-dep}
    Bachant P, Wosnik M. {UNH-RVAT} {R}eynolds number dependence experiment:
    Reduced dataset and processing code; 2016.
    \newblock fig\textbf{share}.
    \url{http://dx.doi.org/10.6084/m9.figshare.1286960}.

    \bibitem{Bachant2015-JoT}
    Bachant P, Wosnik M.
    \newblock Characterising the near-wake of a cross-flow turbine.
    \newblock Journal of Turbulence. 2015 January;16(4):392--410.

    \bibitem{Bachant2016-RM2-data}
    Bachant P, Wosnik M, Gunawan B, Neary V. {UNH} {RM2} tow tank experiment:
    Reduced dataset and processing code; 2016.
    \newblock fig\textbf{share}. http://dx.doi.org/10.6084/m9.figshare.1373899.

    \bibitem{Strickland1981}
    Strickland J, Smith T, Sun K.
    \newblock A Vortex Model of the Darrieus Turbine: An Analytical and
    Experimental Study.
    \newblock Lubbock, {TX}: Texas Tech University; 1981. SAND81-7017.

    \bibitem{Laneville1986}
    Laneville A, Vittecoq P.
    \newblock Dynamic Stall: The Case of the Vertical Axis Wind Turbine.
    \newblock Journal of Solar Energy Engineering. 1986 May;108:140--145.

    \bibitem{Mays1990}
    Mays ID, Morgan CA, Anderson MB, Powles SJR.
    \newblock Experience with the {VAWT} 850 demonstration project.
    \newblock In: Proceedings of European Community Wind Energy Conference; 1990. .

    \bibitem{Roh2013}
    Roh SC, Kang SH.
    \newblock Effects of a blade profile, the {R}eynolds number, and the solidity
    on the performance of a straight bladed vertical axis wind turbine.
    \newblock Journal of Mechanical Science and Technology. 2013;.

    \bibitem{Bedon2014}
    Bedon G, Antonini EGA, Betta SD, Castelli MR, Benini E.
    \newblock Evaluation of the different aerodynamic databases for vertical axis
    wind turbine simulations.
    \newblock Renewable and Sustainable Energy Reviews. 2014;40.

    \bibitem{Sheldahl1977}
    Sheldahl RE, Blackwell BF.
    \newblock Free-Air Performance Tests of a 5-Metre-Diameter Darrieus Turbine.
    \newblock Sandia Laboratories; 1977.

    \bibitem{Antheaume2008}
    Antheaume S, Maıtre T, Achard JL.
    \newblock Hydraulic Darrieus turbines efficiency for free fluid flow conditions
    versus power farms conditions.
    \newblock Renewable Energy. 2008;33:2186--2198.

    \bibitem{Worstell1978}
    Worstell MH.
    \newblock Aerodynamic Performance of the 17 Meter Diameter {Darrieus} Wind
    Turbine.
    \newblock Sandia National Laboratories; 1978. SAND78-1737.

    \bibitem{Para1988}
    Paraschivoiu I.
    \newblock Double-Multiple Streamtube Model for Studying Vertical-Axis Wind
    Turbines.
    \newblock J Propulsion. 1988;4:370--377.

    \bibitem{Orlandi2015}
    Orlandi A, Collu M, Zanforlin S, Shires A.
    \newblock {3D} {URANS} analysis of a vertical axis wind turbine in skewed
    flows.
    \newblock J Wind Eng Ind Aerodyn. 2015;147:77--84.

    \bibitem{Ashwill1992}
    Ashwill TD.
    \newblock Measured Data for the {S}andia 34-Meter Vertical Axis Wind Turbine.
    \newblock Albuquerque, NM 87185: Sandia National Laboratories; 1992.
    SAND91-2228.

    \bibitem{Liu1992}
    Liu WQ, Paraschivoiu I, Martinuzzi R.
    \newblock Calculation of Dynamic Stall on {S}andia 34-M {VAWT} Using an
    Indicial Model.
    \newblock Wind Engineering. 1992;.

    \bibitem{Ponta2001}
    Ponta FL, Jacovis PM.
    \newblock A vortex model for Darrieus turbine using finite element techniques.
    \newblock Renewable Energy. 2001;24:1--18.

    \bibitem{Scheurich2011b}
    Scheurich F, Fletcher TM, Brown RE.
    \newblock Simulating the aerodynamic performance and wake dynamics of a
    vertical-axis wind turbine.
    \newblock Wind Energ. 2011;14:159--177.

    \bibitem{Amet2009}
    Amet E, Maitre T, Pellone C, Achard JL.
    \newblock {2D} Numerical Simulations of Blade-Vortex Interaction in a
    {D}arrieus Turbine.
    \newblock Journal of Fluids Engineering. 2009 November;131.

    \bibitem{Howell2010}
    Howell R, Qin N, Edwards J, Durrani N.
    \newblock Wind tunnel and numerical study of a small vertical axis wind
    turbine.
    \newblock Renewable Energy. 2010;35:412--422.

    \bibitem{Joo2015}
    Joo S, Choi H, Lee J.
    \newblock Aerodynamic characteristics of two-bladed H-Darrieus at various
    solidities and rotating speeds.
    \newblock Energy. 2015;p. 1--13.

    \bibitem{Mertens2003}
    Mertens S, van Kuik G, van Bussel G.
    \newblock Performance of an {H}-{D}arrieus in the skewed flow on a roof.
    \newblock Journal of Solar Energy Engineering. 2003;125:443--440.
    \newblock Available from:
    \url{https://www.researchgate.net/profile/Gerard_Van_Bussel/publication/245367769_Performance_of_an_H-Darrieus_in_the_Skewed_Flow_on_a_Roof/links/0deec53bc12ee39ec4000000.pdf}.

    \bibitem{Bachant2014-RVAT-baseline}
    Bachant P, Wosnik M. {UNH-RVAT} baseline performance and near-wake
    measurements: Reduced dataset and processing code; 2014.
    \newblock fig\textbf{share}. http://dx.doi.org/10.6084/m9.figshare.1080781.
    \newblock Available from: \url{http://dx.doi.org/10.6084/m9.figshare.1080781}.

    \bibitem{Michelen2014}
    Michelen C, Neary VS, Murray JC, Barone M.
    \newblock {CACTUS} open source code for hydrokinetic turbine design and
    analysis: model performance evaluation and public dissemination as open
    source design tool.
    \newblock In: Proceedings of the 2nd Marine Energy Technology Symposium; 2014.
    .

    \bibitem{Bachant2016-Energies}
    Bachant P, Wosnik M.
    \newblock Effects of Reynolds Number on the Energy Conversion and Near-Wake
    Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine.
    \newblock Energies. 2016;9(73).

    \bibitem{Bachant2015-RM2-CAD}
    Bachant P, Wosnik M, Gunawan B, Neary V. 1:6 scale {RM2} cross-flow turbine
    {CAD} package; 2015.
    \newblock fig\textbf{share}. http://dx.doi.org/10.6084/m9.figshare.1373870.

    \bibitem{Beam2011}
    Beam MJ, Elbing BR, Fetterolf TK, Kline BL, Kerstetter DF, Mickey JA, et~al.
    \newblock Power Take-Off System Design {SNL} Reference Turbine 2.
    \newblock Penn State Applied Research Lab; 2011.

    \bibitem{Fiedler2009}
    Fiedler AJ, Tullis S.
    \newblock Blade Offset and Pitch Effects on a High Solidity Vertical Axis Wind
    Turbine.
    \newblock Wind Engineering. 2009;33:237--246.

    \bibitem{SentranZB}
    Sentran. {ZB} {S} Beam Load Cell Datasheet; 2014.
    \newblock \url{http://www.sentranllc.com/pdfs/zb1.pdf}.
    \newblock Available from: \url{http://www.sentranllc.com/pdfs/zb1.pdf}.

    \bibitem{InterfaceT8}
    {Interface Inc }. T8 General Purpose Rotary Torque Transducer Specifications;
    2014.
    \newblock
    \url{http://www.interfaceforce.com/index.php?T8-General-Purpose-Rotary-Torque-Transducer&mod=product&show=65}.
    \newblock Available from:
    \url{http://www.interfaceforce.com/index.php?T8-General-Purpose-Rotary-Torque-Transducer&mod=product&show=65}.

    \bibitem{KollmorgenAKD}
    Kollmorgen. {AKD} user guide; 2014.
    \newblock
    \url{http://www.kollmorgen.com/en-us/products/drives/servo/akd/_manuals/kollmorgen-akd-user-guide-en-rev-m/}.
    \newblock Available from:
    \url{http://www.kollmorgen.com/en-us/products/drives/servo/akd/_manuals/kollmorgen-akd-user-guide-en-rev-m/}.

    \bibitem{RenishawLM15}
    Renishaw. {LM}15 linear encoder datasheet; 2014.
    \newblock
    \url{http://resources.renishaw.com/download.aspx?lang=en&data=49238&btn=1}.
    \newblock Available from:
    \url{http://resources.renishaw.com/download.aspx?lang=en&data=49238&btn=1}.

    \bibitem{NortekVectrino}
    Nortek-{AS}. Vectrino 3{D} water velocity sensor lab probe datasheet; 2014.
    \newblock
    \url{http://www.nortekusa.com/lib/data-sheets/datasheet-vectrino-lab}.
    \newblock Available from:
    \url{http://www.nortekusa.com/lib/data-sheets/datasheet-vectrino-lab}.

    \bibitem{ColemanSteele}
    Coleman HW, Steele WG.
    \newblock Experimentation, Validation, and Uncertainty Analysis for Engineers.
    \newblock 3rd ed. John Wiley \& Sons,; 2009.

    \bibitem{Cavagnaro2014}
    Cavagnaro R, Polagye B.
    \newblock An Evaluation of Blockage Corrections for a Helical Cross-Flow
    Turbine.
    \newblock In: Proceedings of the 3rd Oxford Tidal Energy Workshop. Oxford, UK;
    2014. .

    \bibitem{Lissaman1983}
    Lissaman PBS.
    \newblock Low-{R}eynolds-number airfoils.
    \newblock Annual Review of Fluid Mechanics. 1983;15:223--239.

    \bibitem{McMasters1980}
    McMasters JH, Henderson ML.
    \newblock Low-speed single-element airfoil synthesis.
    \newblock Tech Soaring. 1980;6(2):1--21.

    \bibitem{Migliore1980}
    Migliore PG, Wolfe WP, Fanucci JB.
    \newblock Flow Curvature Effects on {D}arrieus Turbine Blade Aerodynamics.
    \newblock J Energy. 1980;4(2):49--55.

    \bibitem{Goude2012}
    Goude A.
    \newblock Fluid Mechanics of Vertical Axis Turbines, Simulations and Model
    Development.
    \newblock Uppsala University; 2012.

    \bibitem{Rawlings2008}
    Rawlings GW.
    \newblock Parametric characterization of an experimental vertical axis hydro
    turbine.
    \newblock University of British Columbia; 2008.

    \bibitem{Templin1974}
    Templin RJ.
    \newblock Aerodynamic performance theory for the NRC vertical axis wind
    turbine.
    \newblock Ottawa, Canada: National Research Council Canada; 1974. LTR-LA-160.

    \bibitem{Kinzel2012}
    Kinzel M, Mulligan Q, Dabiri JO.
    \newblock Energy exchange in an array of vertical-axis wind turbines.
    \newblock Journal of Turbulence. 2012;13:1--13.

\end{thebibliography}
